Consistent Polyhedral Surrogates via Embedding

### 2019-11-01 notes/top-k.tex
Beginning of proof that \R is correct... but it has a big hole.

\subsection{Notation and Assumptions}
\subsubsection{Notation}
We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_{[i]}$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $y^{th}$ element, respectively.
%Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
%See below in Section~\ref{sec:assumptions} for justification.
%If each $u_i \leq 1$, then we assign $b = 0$.

%We use $\odot$ to denote the Hadamard (element-wise) vector product.
Let $\min(\vec w, \vec v) \in \reals^d$ denote the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.

\subsubsection{Assumptions}\label{sec:assumptions}
Throughout, we make three assumptions about our report set. 
For all $p \in \simplex$, we show there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ satisfying the latter two assumptions; the first assumption is simply for ease of exposition.

\begin{assumption}\label{assum:ordered-u}
First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
\end{assumption}
This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
This is simply for ease of exposition, as it allows us to write $u_i$ instead of $u_{[i]}$ in many situations.

For our second assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
\begin{lemma}
	For all $\alpha \in \reals$ and $y\in\Y$, we have $L^{top-k}(u)_y = L^{top-k}(u + \alpha \ones)_y$.
\end{lemma}
\begin{proof}\label{lem:invar-ones}
	\begin{align*}
	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha \ones  - e_y)_{[i]} \right)_+\\
	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= L^{top-k}(u)_y
	\end{align*}
\end{proof}

\begin{assumption}\label{assum:nonneg}
	We will say $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
\end{assumption}
This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
We set $u_{k+1} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.

\begin{lemma}\label{lem:extra-elts-zero}
%  \raf{This statement seems off.  I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
	For all $u \in \reals^d$ satisfying Assumption~\ref{assum:ordered-u}, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:invar-ones}, we can fix $u_{k+1} = 0$.
	With Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
	Consider $u'$ such that $u'_i = u_i$ for all $i$ so that $u_i \geq 0$, and $u'_i = 0$ otherwise.

	If $y \geq k+1$, then 
	\begin{align*}
	L^{top-k}(u)_y &= (1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]})_+ \\
%	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
	&\geq \left(1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}
	The inequality comes from the equality of the first $k+1$ elements of $u$ and $u'$, combined with the assumption that $u_y \leq u'_y = 0$ in this case.

	Now, if $y < k+1$ and $u_y \geq 1$, then 
	\begin{align*}
	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\right)_+ \\
	&= \left(1 - u_y + \bar u - \frac 1 k\right)_+\\
	&= \left(1 - u'_y + \bar u' - \frac 1 k\right)_+\\
	&= L^{top-k}(u')~.~
	\end{align*}

	Now suppose that $y < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{k+1} = 0$. 
	\begin{align*}
	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^{k-1} u_{[i]} + 0 \right)_+\\
	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k-1} u'_{[i]}\right)_+\\
	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k} (u' - e_y)_{[i]}\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}

@@

\begin{lemma}\label{lem:top-threshold}
	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumptions~\ref{assum:ordered-u} and~\ref{assum:nonneg} so that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$. 
\end{lemma}
\begin{proof}
	Reassigning such a $u'_i := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.

To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i$ for all $i \neq y$. 
\begin{align*}
L^{top-k}(u)_y &= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} + \epsilon\right) \right)_+\\ 
&= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} + \epsilon\right) \right)_+\\
&= \left(-\bar u_{-y} - \epsilon + \bar u_{-y} + \frac \epsilon k \right)_+ \\
&= (-\frac{k-1}{k}\epsilon)_+\\
&= 0
\end{align*}
Compare the above to the following:
\begin{align*}
L^{top-k}(u')_y &= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} \right) \right)_+\\ 
&= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} \right) \right)_+\\
&= \left(-\bar u_{-y} + \bar u_{-y}\right)_+ \\
&= 0~.~
\end{align*}
Thus, the losses are equal on the outcome $y$ where $u_y > \bar u_{-y} + 1$.

Now let us consider outcome $j \neq y$.
By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $y < k+1$ as $u_y > 0$.
Now, for outcome $j \neq y$, we have 
\begin{align*}
L^{top-k}(u)_j &= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u-e_j)_{[i]} \right)_+\\
	&= \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+\\
	&> \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]}\right)_+\\
	&= L^{top-k}(u')_j
\end{align*}
Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$ for each $y \in \Y$, so we can say the same of the expected loss $\inprod{p}{L^{top-k}(\cdot)}$ for all $p \in \simplex$.
\end{proof}

This leads to our final assumption.
\begin{assumption}\label{assum:top-threshold}
	We restrict to $u$ such that for all $u_i$, we have $u_i \leq \bar u_{-i} +1$.
\end{assumption}

\section{Re-writing the loss}
The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, and ~\ref{assum:top-threshold}.
That is, 
\begin{align*}
\U := \{ u \in \reals^n : \bar u_1 + 1 \geq u_1 \geq u_2 \geq \ldots \geq u_k \geq 0 = u_{k+1} = \ldots = u_n \}~.~
\end{align*}
\jessie{this is wrong... doesn't have $u_2 \leq \bar u_{-2}+1$... at least not trivially.}

\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.  Then we can say $u\in\U$ and forget the assumptions going forward.}

\begin{lemma}\label{lem:get-rid-max-op}
	For all $u \in \U$, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
\end{lemma}
This statement allows us to consider the loss $L^{top-k}$ without the $(\cdot)_+$ operator, since the inside term being nonnegative implies the max of the term and $0$ is always the inside term.
\begin{proof}
	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$.
	Moreover, we need to show that $u_y \leq 1 + \frac 1 k \sum_{i=1}^k (u-e_y)_{[i]}$.

	If $y \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
	This holds since $u_y \leq u_k \leq \bar u \leq 1 + \bar u$ by Assumption~\ref{assum:ordered-u}.

	Now if $y < k+1$ and $u_y \in [0,1]$, then we have $(u-e_y)_{[k]} = 0$, and the above term becomes
	\begin{align*}
	&1 -u_y + \frac{1}{k} \sum_{i=1}^{k} u_i - \frac 1 k u_y \geq 0\\
	&\iff 1 + \bar u \geq u_y + \frac{1}{k} u_y\\
	&\iff 1 + \frac k {k-1} \bar u_{-y} \geq u_y~,~
	\end{align*}
	which is true by Assumption~\ref{assum:nonneg}, since this implies $\frac{k}{k-1} \bar u_{-y}$ is nonnegative.

@@

	Therefore, the term is nonnegative if $u$ satisfies Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}.
\end{proof}

With Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can know re-write the loss for each outcome in a simplified form.
\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}
\begin{lemma}\label{lem:new-form-surrogate}
	For $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, the top-$k$ surrogate can be re-written:
\begin{align*} 
L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1))~.~
\end{align*}
\end{lemma}
\begin{proof}
	First, consider
\begin{align*}
	L^{top-k}(u)_y &= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= 1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]}~,
	\end{align*}
	by Lemma~\ref{lem:get-rid-max-op}.

@@

\begin{lemma}\label{lem:linear-pieces}
	For each element $u_i$ of $u$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
	\jessie{Not sure if this is the right statement.}
    \raf{Not sure either.  One thing to be careful about: you either have to make sure that the intervals in question yield points in the set $\U$, or refer to the original form of the loss.  Because the form of the loss you are using only is shown to hold when $u\in\U$.  Hopefully that made sense.}
    \raf{One thing that would help: let's visualize $\U$ for some value of $k,n$ to get some intuition for what this set is.  Maybe $k=2$ and $n=3$, but only plot the first 2 coordinates?}
\end{lemma}
\begin{proof}
	For all $p \in \simplex$ and $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, we know that 
	\begin{equation}
	\inprod{p}{L^{top-k}(u)} = 1 - \bar u + \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
	\end{equation}
	For any $p$, if $u_i \in [0,1]$, we then have 
	\begin{align*}
	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}\\
	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
	\end{align*}
	which is linear on $u_i$.

>>>>

\subsection{Notation and Assumptions}
\subsubsection{Notation}
We say $u_{[i]}$ is the $i^{th}$ largest element of the $u$ vector.
Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_{[i]}$ and similarly, $\bar{u}_{-i} = \frac{1}{k-1} (k \bar u - u_{[i]})$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k-1$ sorted elements of $u$ besides the $i^{th}$ element, respectively.
$u[y]$ refers to the order of the $y^{th}$ component of $u$.
For example, if $u = (1,2,0)$, then $[2] = 1$. 
If $u$ is understand from context, we abuse notation to omit the $u$ and write $u[y] = [y]$.

Let $\min(\vec w, \vec v) \in \reals^d$ denote the element-wise minimum of vectors $\vec w, \vec v \in \reals^d$.

\subsubsection{Assumptions}\label{sec:assumptions}
Throughout, we make two assumptions about our report set. 
For all $p \in \simplex$, we show there is a minimizer of $\inprod{p}{L^{top-k}(\cdot)}$ satisfying these two assumptions.

%\begin{assumption}\label{assum:ordered-u}
%First, assume that $u$ is ordered, where $u_1 \geq u_2 \geq \ldots \geq u_n$.
%\end{assumption}
%This is without loss of generality, as we can reorder $p$ so that each $p_i$ corresponds to the ordered $u_i$ that it originally corresponded to.
%This is simply for ease of exposition, as it allows us to write $u_i$ instead of $u_{[i]}$ in many situations.

For our first assumption, we first observe that $L^{top-k}$ is invariant in the $\ones$ direction.
\begin{lemma}
	For all $\alpha \in \reals$ and $y\in\Y$, we have $L^{top-k}(u)_y = L^{top-k}(u + \alpha \ones)_y$.
\end{lemma}
\begin{proof}\label{lem:invar-ones}
	\begin{align*}
	L^{top-k}(u + \alpha \ones)_y &= \left(1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha \ones  - e_y)_{[i]} \right)_+\\
	&= \left(1 - (u_y + \alpha) +\frac{1}{k} \alpha k + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y - \alpha + \alpha + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= L^{top-k}(u)_y
	\end{align*}
\end{proof}

\begin{assumption}\label{assum:nonneg}
	We will say $u_{[k+1]} = \ldots = u_{[n-1]} = u_{[n]} = 0$.
\end{assumption}
This partially follows from the invariance of $L^{top-k}$ in the $\ones$ direction shown in Lemma~\ref{lem:invar-ones}.
We set $u_{[k+1]} = 0$, and then show weak dominance of the nonnegative $u'$ over any $u$ that contains negative components as in Lemma~\ref{lem:extra-elts-zero}.

\begin{lemma}\label{lem:extra-elts-zero}
%  \raf{This statement seems off.  I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
	For all $u \in \reals^d$, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:invar-ones}, we can fix $u_{[k+1]} = 0$.
	We then have $u_{[i]} \leq 0$ for all $i \geq k+1$.
	Consider $u'$ such that $u'_{[i]} = u_{[i]}$ for all $i$ so that $u_{[i]} \geq 0$, and $u'_{[i]} = 0$ otherwise.
	Observe that $u$ and $u'$ have the same ordering on their elements.

	If $[y] \geq k+1$, then 
	\begin{align*}
	L^{top-k}(u)_y &= (1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]})_+ \\
%	&= 1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\\
	&\geq \left(1 + \frac {1}{k} \sum_{i=1}^k (u' - e_y)_{[i]}\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}
	The inequality comes from the equality of the first $k+1$ sorted elements of $u$ and $u'$, combined with setting $u_{[y]} \leq u'_{[y]} = 0$ in this case.

	Now, if $[y] < k+1$ and $u_y \geq 1$, then 
	\begin{align*}
	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u - e_y)_{[i]}\right)_+ \\
	&= \left(1 - u_y + \bar u - \frac 1 k\right)_+\\
	&= \left(1 - u'_y + \bar u' - \frac 1 k\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}

	Now suppose that $[y] < k+1$ and $u_y \in [0,1)$; we now observe $(u - e_y)_{[k]} = u_{[k+1]} = 0$. 
	\begin{align*}
	L^{top-k}(u)_y &= \left(1 - u_y + \frac 1 k \sum_{i=1}^{k-1} u_{[i]} + 0 \right)_+\\
	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k-1} u'_{[i]}\right)_+\\
	&= \left(1 - u'_y + \frac 1 k \sum_{i=1}^{k} (u' - e_y)_{[i]}\right)_+\\
	&= L^{top-k}(u')_y~.~
	\end{align*}

@@

\begin{lemma}\label{lem:top-threshold}
	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:nonneg} so that for all $i$, we have $u_i \leq \bar u_{-i} +1$. 
\end{lemma}
\begin{proof}
	If $u_{[i]} > \bar u_{-i} + 1$, reassigning such a $u'_{[i]} := \bar u_{-i} +1$ results in $L^{top-k}(u')_i = L^{top-k}(u)_i = 0$, but we observe $L^{top-k}(u')_j \leq L^{top-k}(u)_j$ for all $j \neq i$ by decreasing $\ubar$, since $u_i \geq 0$.

To see this, consider $u_y = \bar u_{-y} + 1 + \epsilon$ and $u'_y = \bar u_{-y} + 1$, with $u_i = u'_i$ for all $i \neq y$. 
\begin{align*}
L^{top-k}(u)_y &= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} + \epsilon\right) \right)_+\\ 
&= \left(1 - (\bar u_{-y} + \epsilon + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} + \epsilon\right) \right)_+\\
&= \left(-\bar u_{-y} - \epsilon + \bar u_{-y} + \frac \epsilon k \right)_+ \\
&= (-\frac{k-1}{k}\epsilon)_+\\
&= 0
\end{align*}
Compare the above to the following:
\begin{align*}
L^{top-k}(u')_y &= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left(\sum_{i=1, i \neq y}^k u_i + \bar u_{-y} \right) \right)_+\\ 
&= \left(1 - (\bar u_{-y} + 1) + \frac 1 k \left((k-1) \bar u_{-y} + \bar u_{-y} \right) \right)_+\\
&= \left(-\bar u_{-y} + \bar u_{-y}\right)_+ \\
&= 0~.~
\end{align*}
Thus, the losses are equal on the outcome $y$.

Now let us consider outcome $j \neq y$.
By Assumption~\ref{assum:nonneg}, if $u_y > \bar u_{-y} + 1$, then we have $[y] < k+1$ as $u_y > 0$.
Moreover, $u_y \geq 1$ in this case.
Now, for outcome $j \neq y$, we have 
\begin{align*}
L^{top-k}(u)_j &= \left( 1 - u_j + \frac 1 k \sum_{i=1}^k (u-e_j)_{[i]} \right)_+\\
	&= \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]} + \frac {\epsilon}{k}\right)_+\\
	&> \left( 1 - u'_j + \frac 1 k \sum_{i=1}^k (u'-e_j)_{[i]}\right)_+\\
	&= L^{top-k}(u')_j
\end{align*}
Therefore, if $u$ minimizes $L^{top-k}(\cdot)_y$, then so does $u'$ for each $y \in \Y$, so we can say the same of the expected loss $\inprod{p}{L^{top-k}(\cdot)}$ for all $p \in \simplex$.
\end{proof}

This leads to our final assumption.
\begin{assumption}\label{assum:top-threshold}
	We restrict to $u$ such that for all $i$, we have $u_i \leq \bar u_{-i} +1$.
\end{assumption}

\section{Re-writing the loss}
The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.

One can observe that $\U$ is not convex.
However, we can consider permutations $\pi$ of the elements of $\U$ so that $\pi(u)$ is the permutation of $\{1,2,\ldots, n\}$ so that $u$ is ordered in decreasing order according to this permutation.
We then let $\U_\pi$ be all $u \in \reals^d$ ordered by the same $\pi$ of $\{1,2,\ldots,n\}$.
Now regrardless of $\pi$, we can consider $\U \cap \U_\pi$, which is a convex set, and every $u \in \U$ is also in $\U \cap \U_{\pi}$ for some $\pi$.

%Moreover, we relax Assumption~\ref{assum:nonneg} to the following.
%\begin{assumption}\label{assum:nonneg-relax}
%	$u \in \reals^n_+$.
%\end{assumption}
%In a similar vein, we call $\U^\circ$ the set of $u \in \reals^n$ satisfying Assumptions~\ref{assum:top-threshold} and \ref{assum:nonneg-relax}.
%
%\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.  Then we can say $u\in\U$ and forget the assumptions going forward.}

\begin{lemma}\label{lem:get-rid-max-op}
	For all $u \in \U$, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
\end{lemma}
This statement allows us to consider the loss $L^{top-k}$ without the $(\cdot)_+$ operator, since the inside term being nonnegative implies the max of the term and $0$ is always the inside term.

\begin{proof}
	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$ in Assumption~\ref{assum:nonneg}.
	Moreover, we need to show that $u_y \leq 1 + \frac 1 k \sum_{i=1}^k (u-e_y)_{[i]}$.

	If $[y] \geq k+1$, then $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} = \bar u$, so the inequality becomes $u_y \leq 1 + \bar u$.
	This holds since $u_{[y]} \leq u_{[k]} \leq \bar u \leq 1 + \bar u$.

	Now if $[y] < k+1$ and $u_y \in [0,1]$, then we have $(u-e_y)_{[k]} = 0$, and the above term becomes
	\begin{align*}
	&1 -u_y + \frac{1}{k} \sum_{i=1}^{k} u_i - \frac 1 k u_y \geq 0\\
	&\iff 1 + \bar u \geq u_y + \frac{1}{k} u_y\\
	&\iff 1 + \frac k {k-1} \bar u_{-y} \geq u_y\\
	&\implies \frac k {k-1} \bar u_{-y} \geq 0~,~
	\end{align*}
	which is true by Assumption~\ref{assum:nonneg}.

@@

	Therefore, the term is nonnegative if $u$ satisfies Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold}.
\end{proof}

With Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can now rewrite the loss for each outcome in a simplified form.
\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}\jessie{I'm not sure where?  I don't see it.}
\begin{lemma}\label{lem:new-form-surrogate}
	For $u \in \U \cap \U_{\pi(u)}$, the top-$k$ surrogate can be written:
\begin{align*} 
L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) = \begin{cases}
1 - u_y + \bar u - \frac{u_y}{k} & u_y \leq 1\\
1 - u_y + \bar u - \frac{1}{k} & u_y > 1
\end{cases}
~.~
\end{align*}
\end{lemma}
\begin{proof}
	First, consider
\begin{align*}
	L^{top-k}(u)_y &= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= 1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]}~,
	\end{align*}
	by Lemma~\ref{lem:get-rid-max-op}.

@@

\bigskip
\hrule
\bigskip

Consider the following finite set.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$.

We claim that there are a finite number of polytopes $P^{a} \subseteq \U$ so that (i.) $\cup_{a \in \I} P^{a} = \U$, (ii.) each $P^{a}$ is the convex hull of points in $\R$, and (iii.) $L^{top-k}(\cdot)_y$ is linear on each $P^{a}$ for each $y \in \Y$.
If these three statements are true, then $L^{top-k}|_\R$ is embedded by $L^{top-k}$.

First, fix a permutation $\pi$ on the elements of $\{1,2,\ldots, n\}$.
Consider $u \in \U \cap \U_\pi$ ordered by $\pi$.
Define the polytopes $P^\pi_a := \{u \in \U\cap \U_\pi : u_i \in [0,1] \text{ or } u_i > 1\}$, for some choice of inequality for each $i \in [n]$.
One can observe there are only a finite number of such polytopes as there are only finitely many permutations $\pi$ of $\{1,2,\ldots, n\}$.
Moreover, there are only finitely many ($2^n$) ways to assign $a_j = \{u_i \in \{[0,1], (1, \bar u_{-i} + 1]\} \}$ for all $i$, and therefore there are only finitely many polytopes.

For all $u \in P^\pi_a$, we have $c(u)$ constant, as $M(u)$ and $H(u)$ are constant in this polytope by design.

Iterating over each choice of inequality $a \in \mathcal{A}$, where $\mathcal{A}$ is the choice of valuations on $u_i$ for all $i$, obeying the permutation ordering, we union to $\U \cap \U_\pi$.  
Since this holds for every permutation, and all the permutations union to the entire space $\U$, as $\cup_\pi(\U \cap \U_\pi) = \U \cap (\cup_\pi \U_\pi) = \U \cap \reals^n = \U$.  
If this is true for every permutation $\pi$, then it holds for $\U$; hence we satisfy (i.).

\jessie{I'm not sure how to modify so that (ii.) is true... consider $n=3, k=2$ and $u = (2.01, 1.01, 0)$.  This is in $\U$, but is not in the convex hull of points in $\R$, since $\R$ only goes out to $2$ in any given direction here.  We might need to also intersect with $[0,k]^n$?  This seems hard to prove though.  Not sure if this is the exact restriction...}
To see (ii.), fix $a$ for some choice of $u_i \in [0,1]$ or $u_i >1$ for all $i$.
For each $i$, consider that $u_i \in [0,1]$ implies $u_1 \in \conv(\{0,1\})$; both elements are members of $\R$.
Similarly, $u \in \U$ and $u_i \in [1,\bar u_{-i}+1]$ implies  $u_i \in \conv(\{1, \bar u_{-i} + 1\})$, which are both members of $\R$ \jessie{this statement is not true...}.

As $\conv(\times_{j=1}^n a_j) = \times_{j=1}^n \conv(a_j)$ where $a_j$ denotes each component of $a$, we then have the desired result (ii.).

%To see (ii.), we first know this is true for $u \in [0,1]^n$ by construction of the polytope, as this polytope is defined by $u$ obeying the permutation $\pi$, which has a linear boundary defined by $\vec 0$ and an edge of the $\{0,1\}^n$ hypercube.
%
%For $u \not \in [0,1]^n$, consider the boundary of the polytope to be $\{u \in \U \cap \U_\pi : u_i >1 \implies u_i = \bar u_{-i} + 1\}$.
%\jessie{Not sure on this part.}

To see (iii.), we claim that $L^{top-k}(\cdot)_y$ is linear on each polytope $P^\pi_a$.
Consider that on the polytope $P^\pi_a$, we fix $u_y \in [0,1]$ or $u_y >1$ for all $y \in \Y$, so on each piece, $L^{top-k}(\cdot)_y$ is linear when we break the loss down into cases, as we do not switch cases within a polytope since each polytope has $u_i$ fixed in one of the two cases for all $i$.

%For a fixed $u$, take $M$ to be $\{i \in [n] : u_i \in [0,1]\}$ and $H := \{i \in [n] : u_i > 1 \}$.
%
%For each $i$, if $u_i \in [0,1]$, take the set of points $\R'$ such that $u_i \in \R$ such that $u_i \in \{0,1\}$.
%Further, restrict this set $\R'$ to $\R''$ so that for $u_i \in (1, \bar u_{-i} +1]$, $\R'' := \{u \in \R' : u_i \in \{1, c\}\}$, where $c := \frac{|M|+k-1}{k-|H|}$.
%
%We define the polytope $P^u$ to be $\conv(\R'')$, so clearly (ii.) is satisfied, since $\R'' \subseteq \R$.
%
%To see that (i.) is true, \jessie{TODO...}
%
%Lastly, to see that $L^{top-k}$ is linear of each piece $\R''$ of $\U$
%
%\jessie{Thoughts: take $\pi$ to be a permutation.  $\R'(\pi)$ is the set of $u \in \R$ so that $\pi = \pi(u)$, 
%	%and for all $i: u_i > 1$, we have $u \in \R: u_i \in \{1, c\}$ in $\R'(\pi)$, and for $i: u_i \in [0,1]$, we have $u \in \R : u_i \in \{0,1\}\}$ in $\R'(\pi)$
%	$\R'(\pi) = \{r \in \U_\pi \cap \R: u_i >1 \implies r_i \in \{1,c\}, u_i \in [0,1] \implies r_i \in \{0,1\} \}$.
%	
%}

\bigskip
\hrule
\bigskip

\begin{lemma}\label{lem:linear-pieces}
	For each element $u_i$ of $u \in \U$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
	\jessie{Not sure if this is the right statement.}
    \raf{Not sure either.  One thing to be careful about: you either have to make sure that the intervals in question yield points in the set $\U$, or refer to the original form of the loss.  Because the form of the loss you are using only is shown to hold when $u\in\U$.  Hopefully that made sense.}
    \raf{One thing that would help: let's visualize $\U$ for some value of $k,n$ to get some intuition for what this set is.  Maybe $k=2$ and $n=3$, but only plot the first 2 coordinates?}
\end{lemma}
\begin{proof}
	For all $p \in \simplex$ and $u \in \U^\circ$, we know that 
	\begin{equation}
	\inprod{p}{L^{top-k}(u)} = 1 - \bar u + \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
	\end{equation}
	For any $p$, if $u_i \in [0,1]$, we then have 
	\begin{align*}
	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}\\
	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
	\end{align*}
	which is linear on $u_i$.
